Secure Composition of Robust and Optimising Compilers

### 2023-07-09 popl/main.tex
Comment parts of abstract

  Memory safety necessitates secrecy, since breaking it can lead to an arbitrarily large attack space, i.e., from simply reading a secret up to alteration of control--flow in order to execute arbitrary code.
  Secrecy cannot be achieved with just memory safety alone, since private data could be leaked by differences in execution time for varying program inputs.
  This leakage is avoidable by ensuring that programs are cryptographic constant time, i.e., differnt inputs do not change execution time.
  Prior work has shown that strategies to ensure cryptographic constant time can be rendered useless, since a compiler may simply optimize them away.
  This is why secure compilation is an integral ingredient to achieve security, because a secure compiler guarantees (formally) that properties that hold in the source, also hold in the target. %% mention attacker? the text describes correctness

  Unfortunately, it is an open question wether secure compilers can be engineered in a modular way.
  Ideally, compiler engineers develop two different compilation passes, one that ensures memory safety and another one that tackles cryptographic constant time, because this style of engineering is well--established for its simplifying divide--and--conquer approach as well as enhanced reusability.

  This paper answers that question positively: The composition of compilers that are secure with respect to some security--properties yields the intersection of these properties.
  This article discusses different variants of compositions of secure compilers and instantiates parts of these results in a case--study.
  To this end, it presents an optimizing, secure compilation chain that preserves both memory safety and cryptographic constant time.
  Memory safety is achieved by composing secure compilers for both temporal and spatial memory safety, where the compiler for spatial memory safety is an instrumentation that inserts bounds--checks in front of pointer dereferences.
  The compiler for cryptographic constant time exploits the use of a data (operand) timing independent mode and the employed optimisations of the compilation chain are constant folding and dead code elimination.
  The compositionality results enable modular proofs for the whole compilation chain that is secure with respect to both memory safety and cryptographic constant time.
  Parts of the results are verified in the Coq proof assistant.

>>>>

  Memory safety necessitates secrecy, since breaking it can lead to an arbitrarily large attack space, i.e., from simply reading a secret up to alteration of control--flow in order to execute arbitrary code.
  However, secrecy cannot be achieved with just memory safety alone, since, e.g., private data could be leaked by differences in execution time for varying program inputs.
  This leakage is avoidable by ensuring that programs are cryptographic constant time, i.e., different inputs do not change execution time.
  Prior work has shown that strategies to ensure cryptographic constant time can be rendered useless, since a compiler may simply optimize them away.
  This is why secure compilation is an integral ingredient to achieve security, because a secure compiler guarantees (formally) that properties that hold in the source, also hold in the target. %% mention attacker? the text describes correctness

  Unfortunately, it is an open question wether secure compilers can be engineered in a modular way.
  Ideally, compiler engineers develop two different compilation passes, one that ensures memory safety and another one that is security preserving with respect to cryptographic constant time. %, because this style of engineering is well--established for its simplifying divide--and--conquer approach as well as enhanced reusability.

  This paper answers that question positively: The composition of compilers that are secure with respect to some security--properties yields the intersection of these properties.
  This article discusses different variants of compositions of secure compilers and instantiates parts of these results in a case--study.
  To this end, it presents an optimizing, secure compilation chain that preserves both memory safety and cryptographic constant time.
%  Memory safety is achieved by composing secure compilers for both temporal and spatial memory safety, where the compiler for spatial memory safety is an instrumentation that inserts bounds--checks in front of pointer dereferences.
  %The compiler for cryptographic constant time exploits the use of a data (operand) timing independent mode and the employed optimisations of the compilation chain are constant folding and dead code elimination.
  The compositionality results enable modular proofs for the presented, secure compiler. % that is secure with respect to both memory safety and cryptographic constant time.
  Some results of this work are implemented in the Coq proof assistant.
